A generalized definition of multidimensional item response theory parameters

### 2024-03-29 output/paper_draft/paper_M2PLM_parameters.Rmd
Makes preliminary updates to "Test space" section
There are still pending changes to approve, but these are already approved. The remaining ones will be implemented later on, when they are definitively approved.

Let $`r TEST_SPACE`$ be the vector space made up by
the set of $`r DISCR_VECTOR`$ vectors,
with the sum and product by a scalar operations as in $`r REAL_N_SPACE`$.
Consider also an orthonormal basis $`r TEST_SPACE_STD_BASIS`$
in $`r TEST_SPACE`$, such that $`r DISCR_STD_COORDS_ALT_EQ`$.
<!-- #TODO: Continue here -->
Since the response probability must be invariant with respect to
a change of basis,
we must define the coordinates $`r DISCR_STD_COORDS`$ of the parameter vector
$`r DISCR_VECTOR`$ in an orthonormal basis $`r TEST_SPACE_STD_BASIS`$,
such that $`r INVARIANCE_EQ`$.
If we assume that $`r DISCR_VECTOR`$ exists in vector space $`r TEST_SPACE`$,
with coordinates $`r DISCR_COORDS`$ in basis $`r TEST_SPACE_BASIS`$,
then we must define $`r DISCR_COORDS`$ such that

\begin{equation}
  `r DISCR_STD_COORDS_EQ`                                (\#eq:discr-vector-std)
\end{equation}

@@

This shows that discrimination vectors are indeed represented in their own
vector space $`r TEST_SPACE`$ with basis $`r TEST_SPACE_BASIS`$.
We shall refer to this new space as the *test space* [@zhang_theoretical_1999].
Although the inverse relationship between their respective inner product
Gram matrices induces a bijective relationship between the two sets of spaces,
it is worth highlighting that test space $`r TEST_SPACE`$
and latent space $`r LATENT_SPACE`$ are different entities. Only in the
orthonormal case the two spaces share a common inner product
(i.e., the dot product), and thus can be mistaken.

>>>>

Let $`r TEST_SPACE`$ be the vector space made up by
the set of $`r DISCR_VECTOR`$ vectors,
with the sum and product by a scalar operations as in $`r REAL_N_SPACE`$.
Consider also an orthonormal basis $`r TEST_SPACE_STD_BASIS`$
in $`r TEST_SPACE`$, such that $`r DISCR_STD_COORDS_ALT_EQ`$.
Since the response probability to the `r MODEL_ACRONYM`,
given by \@ref(eq:M2PL-formulation), must be invariant with respect to
the change of basis expressed in \@ref(eq:change-basis),
we must define the coordinates $`r DISCR_STD_COORDS`$ of the parameter vector
$`r DISCR_VECTOR`$ in the orthonormal basis $`r TEST_SPACE_STD_BASIS`$,
such that $`r INVARIANCE_EQ`$.
If we assume that $`r DISCR_VECTOR`$ exists in vector space $`r TEST_SPACE`$,
with coordinates $`r DISCR_COORDS`$ in basis $`r TEST_SPACE_BASIS`$,
then we must define $`r DISCR_COORDS`$ such that

\begin{equation}
  `r DISCR_STD_COORDS_EQ`,                               (\#eq:discr-vector-std)
\end{equation}

@@

We shall refer to this new space as the *test space* [@zhang_theoretical_1999].
Although the inverse relationship between their respective inner product
Gram matrices induces a bijective relationship between the two sets of spaces,
it is worth highlighting that test space $`r TEST_SPACE`$
and latent space $`r LATENT_SPACE`$ are different entities. Only in the
orthonormal case the two spaces share a common inner product
(i.e., the dot product), and thus can be mistaken.
